\parth{Question 2 is mine}
Starting from the abstract ket form of the Schrodinger eqn. derive the Schrodinger eqn. in the co-ordinate basis

The Schrodinger eqn. in the abstract ket form is given as follows -
    \begin{align}
        \begin{equation} \label{eq:1}
            \Hamiltonian \, \ket{\psi} = E\, \ket{\psi}
        \end{equation}
    \end{align}
In the position basis, $\Hamiltonian$ can be expressed in the form of a matrix, while $\ket{\psi}$ can be expressed in terms of components in the basis.
In the position basis, the components of $\ket{\psi}$ form the wavefunction.
    \begin{align}
        \begin{equation} \label{eq:2}
            \braket{x}{\psi} = \psi(x).
        \end{equation}
    \end{align}
The Hamiltonian becomes a matrix in the position basis, with components given by -
    \begin{align}
        \begin{equation} \label{eq:3}
            H_{xy} = \bra{x}\Hamiltonian\ket{y}.
        \end{equation}
    \end{align}
Applying this to equation \ref{eq:1}. We multiply by $\bra{x}$ on the left side and insert an identity on the right hand side.
The identity is given by - 
    \begin{align}
        \begin{equation} \label{eq:4}
            1 = \int dy\, \ket{y}\bra{y}
        \end{equation}
    \end{align}
So now we obtain - 
    \begin{align}
        \begin{equation} \label{eq:5}
            \int dy\, \bra{x}\Hamiltonian\ket{y}\braket{y}{\psi} = E \braket{x}{\psi}.
        \end{equation}
    \end{align}
simplifying to components, we get -
    \begin{align}
        \begin{equation} \label{eq:6}
            \int dy \, H_{xy} \psi(y) = E \, \psi(x).
        \end{equation}
    \end{align}
now our components are - 
    \begin{align}
        \begin{equation} \label{eq:7}
            H_{xy} = -\frac{\hbar^2}{2m}\delta''(x-y) + V\delta(x-y)
        \end{equation}
    \end{align}
we plug this in to equation \ref{eq:6}. We get - 
    \begin{align}
        \begin{equation} \label{eq:7}
            \int dy \, -\frac{\hbar^2}{2m}\delta''(x-y) \psi(y) + \int dy \, V\psi(y)\delta(x-y) = E \, \psi(x)
        \end{equation}
    \end{align}
    \begin{align}
        \begin{equation} \label{eq:8}
            \frac{\hbar^2}{2m} \int dy \, \delta''(x-y) \psi(y) + V \psi(x) = E\,  \psi(x)        
        \end{equation}
    \end{align}
Using Integration by Parts on the integral twice, we obtain - 
    \begin{align}
        \begin{equation} \label{eq:9}
            \frac{\hbar^2}{2m} \int dy \, \delta(x-y) \psi''(y) + V \psi(x) = E\,  \psi(x)        
        \end{equation}
    \end{align}
    \begin{align}
        \begin{equation} \label{eq:10}
            \frac{\hbar^2}{2m} \psi''(x) + V\, \psi(x) = E\,  \psi(x)        
        \end{equation}
    \end{align}
Generalising this a bit - 
    \begin{align}
        \begin{equation} \label{eq:11}
            - \frac{\hbar^2}{2m} \nabla^2 \psi + V \psi = E \psi        
        \end{equation}
    \end{align}
This is quite obviously, our Schrodinger's Equation in co-ordinate form.
